---
title: "Homework_1"
author: "Brooke Wheeler"
date: "1/13/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

# 6 Plot the density curve.  Keep in mind that the values of the random variable here must be positive.  Make sure that the x-axis represents F values between 0 and 7 and the y-axis is labeled “density.” 
```{r}
curve(df(x, df1 = 11, df2 = 5), from = 0, to = 7, ylab = "density")
```
# 7 	Find the median value of F. (Hint: keep in mind which percentile the median corresponds to.) Report your answer as F(p;df1,df2)=q, filling in values for p,df1,df2 and q.

# qt gives the quartile value, pt give the area under the curve
# q is the F value while p is the prob under the curve
```{r}
qf(.5, 11, 5)

# F(p;df1,df2)=q  
# F(.5; 11, 5)= 1.08
# There is a 50% chance that an F(11, 5) value will be lower than q=1.08
```

# 8 	4% of values will fall above which value of F? Report your as F(p;df1,df2)=q.
```{r}
qf(.96, 11, 5)

# F(p;df1,df2)=q
# F(.96;11,5)= 5.25
# 4% of values will fall above q=5.25
```

# 9 	Find P(F(11,5)≤3).
```{r}
pf(3,11,5)

# the probability that the value will be below 3 is 88%.
```
 
# 10 	Find P(F(11,5)≥5.25).
```{r}
pf(5.25, 11,5)
1-.96

# The probability that the value will fall above 5.25 is 4%
```








