---
title: "Lab_1"
author: "Brooke Wheeler"
date: "1/12/2022"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
```

# Part One Working with Probability Density Functions

## 1 Plot the density function for the t-distribution with 44 degrees of freedom, or t(44).
```{r}
curve(dt(x,44), from = -4, to = 4, ylab = "density")
```

## 2. 	Find the 75th percentile for the t-distribution with 44 degrees of freedom (df=44).  Report your answer as t(p;df)=q, filling in values for p,df and q.

```{r}
qt(p= .75, df= 44)

# t(.75;44)=.680
```

## 3. 	Consider a t-distribution with df=44.  96% of values will fall between which two values of t (that is find the values that satisfy P(______<t(44)<______=0.96)? Report both answers as t(p;df)=q.

```{r}
qt(p= .02, df= 44)
# t(.02;44)=-2.11

qt(p= .98, df= 44)
#t(.98;44)=2.11

# P(-2.11 <t(44)< 2.11= .96)
```

## 4. 	Consider a t-distribution with df=44.  Find P(t(44)≤-1.5).
```{r}
pt(q=-1.5, df=44)
```

## 5. 	Consider a t-distribution with df=44.  Find P(t(44)≥2).
```{r}
pt(q=2, df= 44)
```


# Part 2: Descriptive Statistics and Basic Graphs

```{r}
getwd()
nationals <- read.table("../Data/nationalsdata2014.csv", header = TRUE, sep = ",")

nationals %>%
  select(Salary)  -> salary
salary
```

## histogram 
```{r}
summary(salary)

hist(nationals$Salary, xlab = "Salary (USD)", main = "Histogram of 2014 Salaries")
```


## boxplot

```{r}

boxplot(nationals$Salary, horizontal = TRUE, main = "Boxplot of 2014 Salaries")
```





