---
title: "hw_3"
author: "Brooke Wheeler"
date: "1/27/2022"
output: pdf_document
---

```{r}
library(tidyverse)
library(ggplot2)
```
## 3. Regression parameters: intercept=200, slope=5
### a. plot regression equation
```{r}
x<-seq(0,10)
plot(x, 200+ 5*x , type = "l", ylab = "y")

200+5*20
200+5*10
200+5*40
```


# Part 2: More properties of the LSRL
## 6. When the residuals are weighted by the level of the predictor variable in the i^th trial, the sum is zero.
```{r}
mass_calories <- read.csv("Mass_Calorie_Data.csv")
attach(mass_calories)

# x=LBM y=rate
reg <- lm(RATE ~ LBM, data = mass_calories)
resid(reg)

sum(LBM * resid(reg))
```

## 7. 	When the residuals are weighted by the predicted/ fitted value in the i^th trial, the sum is zero.
```{r}
reg <- lm(RATE ~ LBM, data = mass_calories)
resid(reg)

sum(predict(reg) * resid(reg))
```

## Part 3 Mini Project

### 8. 
```{r}
gpa <- read.table("CH01PR19.txt")
attach(gpa)
# x= ACT scores y=gpa at end of freshman year
```

#### a. 	Obtain the least squares estimates of β_0  and β_1 and state the estimated regression function.
```{r}
gpa_reg <- lm(V1 ~ V2, data = gpa)
gpa_reg

# the intercept= 2.11405
# the slope is .03883
# yhat= 2.11405 + .03883x
```
#### b. Plot the estimated regression function and the data. Does the estimated regression function   appear to fit the data well?
```{r}
plot(V2, V1)
abline(gpa_reg)

# The estimated regression function does appear to fit the data however there are many outliers.  
```
#### c. 	Obtain a point estimate of the mean freshman GPA for students with ACT test score X = 30.
```{r}

predict(gpa_reg, data.frame(V2= 30))
```

#### d.	What is the point estimate of the change in the mean response when the entrance test score increases by one point?
When the mean test score increases by one point the average gpa increases by .03883

#### e. 	Obtain the residuals e_i.  Show that ∑_(i=1)^n▒〖e_i=0〗  and find ∑_(i=1)^n▒〖e_i〗^2 . 
```{r}
sum(resid(gpa_reg))
# very close to zero

sum((resid(gpa_reg))^2)
# the sum of all residuals squared is 45.81761. This is also called SSE or error sum of squares
```
#### f. Obtain point estimates of σ2 and σ. In what units is each of them expressed (include those units with your answers)?
```{r}
# Error mean square= SSE/n-2
(sum((resid(gpa_reg))^2)) /(120-2)
# estimates of variance squared =.3883, gpa squared

# Standard Error of Estimate
sqrt((sum((resid(gpa_reg))^2)) /(120-2))
# estimates of variance = .623 gpa
```









